### 2022-06-28 input/experiments.tex
almost 20p

\begin{figure*}[t]
  \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
    1157 \processes~\cite{knight2011internet}.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
  }
  \hspace{5pt}
  \subfloat[\label{fig:europe-ases}Traffic overhead and maintained indexes.]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
  }
  \caption{Evaluation of \NAMEC for \emph{lazy} dynamic partitioning.}
\end{figure*}

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
\item[Objective:] Highlight the shortcoming of \NAME in
  infrastructures composed of multiple autonomous systems and
    discuss an improvement called \underline{cross} \underline{\NAME}
    (\NAMEC). At coarse-grained, \NAMEC enables
    \emph{lazy} %\footnote{Laziness properties and \NAMEC would be
    %    further detailed in the  additional two pages available in the
    %    camera-ready version of the article.}
    dynamic partitioning by
    allowing AS' gateways to stop notifications when their respective
    network does not appear to have a source.

  \item[Description:] We build a network of networks comprising
    G{\'E}ANT along with the underlying European NRENs.
    Figure~\ref{fig:nrens} depicts the resulting infrastructure
    composed of 1157 \processes distributed in 40 interconnected
    autonomous systems spanning across
    Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
    in the figure) link autonomous systems together, \eg a Lisbon
    \node links Portugal to Spain and United Kingdoms through a Madrid
    \node and a London \node respectively.

    \noindent Figure~\ref{fig:nrens} also depicts the operations
    executed during the 7 seconds simulation: at 1 second, a \node
    located in Lisbon, Portugal performs an \texttt{Add}, \ie Lisbon
    becomes a new source; at 2 seconds, a \node located in Palma de
    Majorque, Spain performs an \texttt{Add}; at 3 seconds, a \node
    located in Paris, France performs an \texttt{Add}; at 4 seconds, a
    \node located in Hvanneyri, Iceland performs an \texttt{Add};
    finally at 5 seconds, the \node in Spain performs a \texttt{Del},
    \ie the Spanish source is removed. We chose these sources to
    illustrate the limitations of \NAME while further motivating the
    importance of containing the traffic within relevant
    autonomous systems as proposed by \NAMEC.

    \noindent In \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous system, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie adjacent autonomous systems that have at least one
    source.

    \noindent To compare \NAME against \NAMEC, we measure the number
    of messages transiting through the network for each operation, as
    well as the number of \processes that maintain an index (\ie that
    belong to a partition) over time.

  \item[Results:] Figure~\ref{fig:europe-ases} shows the
    results of this experiment. The top part highlights the cost of
    each partitioning protocol after each operation, while the bottom
    part provides the insight that explains these costs by displaying
    the number of indexes maintained by each protocol.

    \noindent Figure~\ref{fig:europe-ases} shows that Portugal's
    \texttt{Add} costs an order of magnitude more with \NAME compared
    to \NAMEC.  \NAME's messages propagate through all Europe, for
    \NAME regards Europe as a single network of 1157 \processes while
    \NAMEC's messages propagate through Portugal's network of 23
    \processes only.
    % 
    \noindent  Spain's
    \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
    gateway in Madrid links Portugal to Spain and the rest of
    Europe. Since Lisbon is closer to Madrid than Palma de Majorque
    is, only 11 \processes in Spain actually need to receive and
    deliver the new notification, which explains the small overhead of this
    operation with \NAME. Using \NAMEC, the overhead is slightly
    higher since
    \begin{inparaenum}[(i)]
    \item the 20 \processes of Spain's network need to receive and
      deliver the new notification, \emph{and}
    \item Madrid's gateway echoes Lisbon's notification as soon as it
      receives Palma's notification to 11 \processes.
    \end{inparaenum}

    \noindent Figure~\ref{fig:europe-ases} also highlights the worst
    case scenario of \NAME: the cost of France's \texttt{Add} is close
    to that of Portugal's \texttt{Add} since it updates the whole
    Europe excluding Portugal and Spain. Contrarily, \NAMEC only
    updates France's 39 \processes.

    \noindent The last \texttt{Add} operation in Iceland has similar
    cost for \NAME and \NAMEC. Indeed, they both update Iceland, and
    when the notifications reach Copenhagen in Danemark, they stop
    either because France's notifications are closer (\NAME) or the
    Danish network does not have any source (\NAMEC).

    \noindent Finally, Figure~\ref{fig:europe-ases} shows that
    Spain's \texttt{Del} have similar cost for \NAME and
    \NAMEC. Nevertheless, the trade-off is different: \NAME's overhead
    comes from the 11 \nodes that need to acknowledge staleness and
    deliver the echos from Portugal; \NAMEC's overhead comes from the
    20 \nodes that need to acknowledge staleness. Using \NAMEC,
    Spain's network does not propagate echos since it does not have
    any source anymore.

>>>>

%% \begin{figure*}[t]
%%   \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
%%     1157 \processes~\cite{knight2011internet}.]{
%%     \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
%%   }
%%   \hspace{5pt}
%%   \subfloat[\label{fig:europe-ases}Traffic overhead and maintained indexes.]{
%%     \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
%%   }
%%   \caption{Evaluation of \NAMEC for \emph{lazy} dynamic partitioning.}
%% \end{figure*}

@@

%% \subsection{Cross autonomous systems}
%% \begin{asparadesc}
%% \item[Objective:] Highlight the shortcoming of \NAME in
%%   infrastructures composed of multiple autonomous systems and
%%     discuss an improvement called \underline{cross} \underline{\NAME}
%%     (\NAMEC). At coarse-grained, \NAMEC enables
%%     \emph{lazy} %\footnote{Laziness properties and \NAMEC would be
%%     %    further detailed in the  additional two pages available in the
%%     %    camera-ready version of the article.}
%%     dynamic partitioning by
%%     allowing AS' gateways to stop notifications when their respective
%%     network does not appear to have a source.

%%   \item[Description:] We build a network of networks comprising
%%     G{\'E}ANT along with the underlying European NRENs.
%%     Figure~\ref{fig:nrens} depicts the resulting infrastructure
%%     composed of 1157 \processes distributed in 40 interconnected
%%     autonomous systems spanning across
%%     Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
%%     in the figure) link autonomous systems together, \eg a Lisbon
%%     \node links Portugal to Spain and United Kingdoms through a Madrid
%%     \node and a London \node respectively.

%%     \noindent Figure~\ref{fig:nrens} also depicts the operations
%%     executed during the 7 seconds simulation: at 1 second, a \node
%%     located in Lisbon, Portugal performs an \texttt{Add}, \ie Lisbon
%%     becomes a new source; at 2 seconds, a \node located in Palma de
%%     Majorque, Spain performs an \texttt{Add}; at 3 seconds, a \node
%%     located in Paris, France performs an \texttt{Add}; at 4 seconds, a
%%     \node located in Hvanneyri, Iceland performs an \texttt{Add};
%%     finally at 5 seconds, the \node in Spain performs a \texttt{Del},
%%     \ie the Spanish source is removed. We chose these sources to
%%     illustrate the limitations of \NAME while further motivating the
%%     importance of containing the traffic within relevant
%%     autonomous systems as proposed by \NAMEC.

%%     \noindent In \NAMEC, each
%%     \process maintains a \emph{local} index that corresponds to the
%%     best partition of its autonomous system, and a \emph{global}
%%     index that corresponds to the best partition cross autonomous
%%     systems, \ie adjacent autonomous systems that have at least one
%%     source.

%%     \noindent To compare \NAME against \NAMEC, we measure the number
%%     of messages transiting through the network for each operation, as
%%     well as the number of \processes that maintain an index (\ie that
%%     belong to a partition) over time.

%%   \item[Results:] Figure~\ref{fig:europe-ases} shows the
%%     results of this experiment. The top part highlights the cost of
%%     each partitioning protocol after each operation, while the bottom
%%     part provides the insight that explains these costs by displaying
%%     the number of indexes maintained by each protocol.

%%     \noindent Figure~\ref{fig:europe-ases} shows that Portugal's
%%     \texttt{Add} costs an order of magnitude more with \NAME compared
%%     to \NAMEC.  \NAME's messages propagate through all Europe, for
%%     \NAME regards Europe as a single network of 1157 \processes while
%%     \NAMEC's messages propagate through Portugal's network of 23
%%     \processes only.
%%     % 
%%     \noindent  Spain's
%%     \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
%%     gateway in Madrid links Portugal to Spain and the rest of
%%     Europe. Since Lisbon is closer to Madrid than Palma de Majorque
%%     is, only 11 \processes in Spain actually need to receive and
%%     deliver the new notification, which explains the small overhead of this
%%     operation with \NAME. Using \NAMEC, the overhead is slightly
%%     higher since
%%     \begin{inparaenum}[(i)]
%%     \item the 20 \processes of Spain's network need to receive and
%%       deliver the new notification, \emph{and}
%%     \item Madrid's gateway echoes Lisbon's notification as soon as it
%%       receives Palma's notification to 11 \processes.
%%     \end{inparaenum}

%%     \noindent Figure~\ref{fig:europe-ases} also highlights the worst
%%     case scenario of \NAME: the cost of France's \texttt{Add} is close
%%     to that of Portugal's \texttt{Add} since it updates the whole
%%     Europe excluding Portugal and Spain. Contrarily, \NAMEC only
%%     updates France's 39 \processes.

%%     \noindent The last \texttt{Add} operation in Iceland has similar
%%     cost for \NAME and \NAMEC. Indeed, they both update Iceland, and
%%     when the notifications reach Copenhagen in Danemark, they stop
%%     either because France's notifications are closer (\NAME) or the
%%     Danish network does not have any source (\NAMEC).

%%     \noindent Finally, Figure~\ref{fig:europe-ases} shows that
%%     Spain's \texttt{Del} have similar cost for \NAME and
%%     \NAMEC. Nevertheless, the trade-off is different: \NAME's overhead
%%     comes from the 11 \nodes that need to acknowledge staleness and
%%     deliver the echos from Portugal; \NAMEC's overhead comes from the
%%     20 \nodes that need to acknowledge staleness. Using \NAMEC,
%%     Spain's network does not propagate echos since it does not have
%%     any source anymore.

%% \end{asparadesc}

### 2022-06-28 input/proposal.tex
almost 20p

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications, even in dynamic networks where nodes join, leave, or
crash at any time. For convenience, Appendix~\ref{appendix:notations}
summarizes the notations used throughout the paper.

@@

\begin{definition}[\label{def:forwarding}Forwarding]
  When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
  \underline{s}ends it ($s_{xy}(m)$) to all its neighbors $y$
  accumulating and aggregating ($\oplus$) metadata that depends on its
  local knowledge $\sigma_x$: $f_x(m) \implies \forall \langle x,
  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
\end{definition}

>>>>

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications, even in dynamic networks where nodes join, leave, or
crash. % at any time. % For convenience, Appendix~\ref{appendix:notations}
% summarizes the notations used throughout the paper.

@@

\begin{definition}[\label{def:forwarding}Forwarding]
  When $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
  \underline{s}ends it ($s_{xy}(m)$) to all its neighbors $y$
  accumulating and aggregating ($\oplus$) metadata that depends on its
  local knowledge $\sigma_x$: $f_x(m) \implies \forall \langle x,
  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
\end{definition}
